---
title: "2024 Little Susitna - Chinook"
author: "Nick DeCovich"
output: html_document
---

```{r setup,warning=FALSE,message=FALSE,include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
##rm(list = ls())
```
```{r packages and functions,include=FALSE}
library(lubridate)
library(WriteXLS)
library(magrittr)
library(dplyr)
library(tidyverse)
library(DT)
source("H:\\Analyses\\L Su Chinook\\Little-Susitna-Chinook/ASL_funs.R")
```



```{r data import csv, include=FALSE}

weir <- read_csv(".///weir.csv", col_types = cols(date = col_date(format = "%Y-%m-%d")))


asl_dat <- read_csv(".///asl_dat.csv",
                    col_types = cols(date = col_date(format = "%Y-%m-%d"),
                                     age = col_character()))

```

```{r strata designation, include=FALSE}
# Determining Strata Dates
# Can change from 1-4 strata, by removing # and adjusting the dates. 
# Using min and max weir data makes the code more transferrable across years and rivers 

#Adjust number of strata and dates 
strat1 <- interval(min(weir$date),ymd("2024-06-27 UTC"))  
strat2 <- interval(ymd("2024-06-28 UTC"),ymd("2024-07-04 UTC"))
strat3 <- interval(ymd("2024-07-05 UTC"), ymd("2024-07-08 UTC"))
strat4 <- interval(ymd("2024-07-09 UTC"), max(weir$date))


#Assign strata to dates within the ASL data sheet

asl_dat$strata <- ifelse( asl_dat$date %within% strat1,1,asl_dat$strata)   
asl_dat$strata <- ifelse( asl_dat$date %within% strat2,2,asl_dat$strata)
asl_dat$strata <- ifelse( asl_dat$date %within% strat3,3,asl_dat$strata)
asl_dat$strata <- ifelse( asl_dat$date %within% strat4,4,asl_dat$strata)   


#Assign strata to dates to match ASL

weir$strata <- ifelse( weir$date %within% strat1,1,weir$strata)   
weir$strata <- ifelse( weir$date %within% strat2,2,weir$strata)
weir$strata <- ifelse( weir$date %within% strat3,3,weir$strata)
weir$strata <- ifelse( weir$date %within% strat4,4,weir$strata)

weir_strata <- 
  weir %>%
  dplyr::group_by(strata) %>%
  dplyr::summarise(total = sum(passage))
weir_sum <- data.frame(total = sum(weir$passage))
```



```{r strata designation2, include=FALSE}
# Add a single strata to use for creating estimates in the event that no strata is indicated

#Adjust number of strata and dates 
strat0 <- interval(min(weir$date),max(weir$date))  


#Assign strata to dates within the ASL data sheet

asl_dat$strata0 <- ifelse( asl_dat$date %within% strat0,1,asl_dat$strata0)   
  
#Assign strata to dates to match ASL

weir$strata0 <- ifelse( weir$date %within% strat0,1,weir$strata0)   

weir_strata0 <- 
  weir %>%
  dplyr::group_by(strata0) %>%
  dplyr::summarise(total = sum(passage))
weir_sum <- data.frame(total = sum(weir$passage))
```

## Chinook ASL

```{r}
knitr::kable(compare_strata(asl_dat, weir, passage)[, c("strata", "asl_dates", "asl_pct", "total_dates", "total_pct")], 
             col.names = c("strata", "asl_dates", "asl_pct", "escapement_dates", "escapement_pct"))
```

```{r, , fig.width = 7, fig.height = 7}
plot_ks(weir, "passage")
ks.test(weir$passage, weir$samples)


```


The sampling was not proportional to the run. We will stratify the sampling according to the operational plan then test for differences in sex and age comp between strata. 


### Chinook sex composition

Likelihood ratio test indicates sex composition *did not* differ between time strata.

```{r}
t.sex<-table(asl_dat$strata,asl_dat$sex)
addmargins(t.sex, c(1, 2))
DescTools::GTest(t.sex)
```

Here is the Chinook sex-length table. We used an un-stratified estimate and met the precision objective.

```{r}
sl <- 
  asl(asl_dat, weir_strata0, groupvars = "strata0") %>% 
  #combine_strata() %>% 
  tab_asl(totalname = "Weir Passage", output = "sl", display_cols = "stat")
knitr::kable(sl)
```

```{r}
ggplot(data=asl_dat,aes(x=length,color=sex))+geom_histogram(aes(y=..density..),bins = 20,position = "identity",alpha=.1)+geom_density(alpha=.2)+scale_x_continuous(breaks=seq(300,1000,100))+
  labs(title="Histogram of length by sex")
```


### Chinook age composition

Likelihood ratio tests indicate age composition *does not* differ between time strata. 

```{r,echo=FALSE}
clean_age <- asl_dat[asl_dat$age %in% c("1.1", "1.2", "1.3","1.4"), ] 
                      
#clean_age$nostrat <- as.numeric("1")
t.age <- table(clean_age$strata,clean_age$age)
lrt=DescTools::GTest(t.age)

noquote("OBSERVED COUNTS")
addmargins(lrt$observed,c(1,2))
cat("\n")
noquote("EXPECTED COUNTS")
expected=as.table(round(lrt$expected))
addmargins(expected,c(1,2))
lrt
```

Here is the Chinook age-length table. We used an un-stratified estimate and met the precision objective.

```{r}
al0 <- asl(clean_age, weir_strata0, groupvars = "strata0")
al<- 
  al0 %>% 
  #combine_strata() %>%
  tab_asl(totalname = "Weir", output = "al", display_cols = "stat")
knitr::kable(al)
```
```{r, echo=F}
ggplot(data=clean_age,aes(x=length,color=age))+geom_histogram(aes(y=..density..),bins = 20,position = "identity",alpha=.1)+geom_density(alpha=.2)+scale_x_continuous(breaks=seq(300,1000,100))+
  labs(title="Histogram of length by Age")
```

### Chinook age-sex composition

Here is the Chinook age-sex-length table.

```{r}
chin_asl <- 
  al0 %>%
  #combine_strata() %>% 
  tab_asl(totalname = "Weir", output = "asl") 
knitr::kable(chin_asl)
```



```{r,warning=FALSE}
library(openxlsx)
#WriteXLS(x = c("sl", "al", "chin_asl"),ExcelFileName = ".//24_LSu_ASL_ND.xlsx",
#                   SheetNames = c("Chinook sex comp", "Chinook age Comp", "Chinook agesex comp"),
#                   AdjWidth = TRUE,
 #                  BoldHeaderRow = TRUE,envir = parent.frame())

WB = createWorkbook("Little Su Chinook ASL 2024")
addWorksheet(WB,"Chinook Sex Comp")
addWorksheet(WB,"Chinook Age Comp")
addWorksheet(WB,"Chinook SexAge Comp")
writeData(WB,sheet = 1,sl,colNames = TRUE)
writeData(WB,sheet = 2,al,colNames = TRUE)
writeData(WB,sheet = 3,chin_asl,colNames = TRUE)
saveWorkbook(WB, ".//24_LSu_ASL_ND.xlsx", overwrite = TRUE)


#write.xlsx(sl,file = ".//22 Deshka ASL_LFW10_4.xlsx",sheetName = "Chinook Sex Comp",colNames = TRUE)
#write.xlsx(al,file = ".//22 Deshka ASL_LFW10_4.xlsx",sheetName = "Chinook Age Comp",append = TRUE)
#write.xlsx(chin_asl,file = ".//22 Deshka ASL_LFW10_4.xlsx",sheetName = "Chinook AgeSex Comp",append = TRUE)

```

# ASL TABLES {.tabset}

## Chinook Sex Comp
```{r,echo=F}

datatable(sl,extensions = "Buttons",
          options=list(
            dom = 'Brtip',
  buttons = c("copy","csv","excel"), scrollX=TRUE,scrollY=TRUE,autoWidth = FALSE))
```
## Chinook Age Comp
```{r,echo=FALSE}
datatable(al,extensions = "Buttons",
          options=list(
            dom = 'Brtip',
  buttons = c("copy","csv","excel"), scrollX=TRUE,scrollY=TRUE,autoWidth = FALSE))
```
## Chinook SexAge Comp
```{r,echo=FALSE}
datatable(chin_asl,extensions = "Buttons",
          options=list(
            dom = 'Brtip',
  buttons = c("copy","csv","excel"), scrollX=TRUE,scrollY=TRUE,autoWidth = FALSE,pageLength=20))
```

# {-}

```{r}
library(downloadthis)
list("Chinook Sex Comp"=sl,"Chinook Age Comp" = al,"Chinook SexAge Comp"=chin_asl)%>%
download_this(button_label = "ASL COMPS EXCEL WORKBOOK",output_extension = ".xlsx",self_contained = TRUE)

```
